---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# effectivenessCalculations

<!-- badges: start -->
<!-- [![CRAN status]()]()
[![License](https://github.com/dzvoti/effectivenessCalculations?tab=MIT-2-ov-file)](https://github.com/dzvoti/effectivenessCalculations?tab=MIT-2-ov-file) -->
[![Version](https://img.shields.io/badge/version-v0.2.0-blue)](https://img.shields.io/badge/version-v0.2.0-blue)
[![Life cycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![R-CMD-check](https://github.com/dzvoti/effectivenessCalculations/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dzvoti/effectivenessCalculations/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of effectivenessCalculations is to provide functions for calculating various metrics related to nutritional effectiveness, such as baseline inadequacy and household reach for food vehicles.

## Installation

You can install the development version of effectivenessCalculations from [GitHub](https://github.com/dzvoti/effectivenessCalculations) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("dzvoti/effectivenessCalculations")
```

## Basic Examples

### Calculate pre and post fortification intake supplies, fortification vehicle reach and Inadequacy Summaries

This is how to calculate the pre and post fortification intake supplies, fortification vehicle reach and Inadequacy Summaries. The function `calculate_pre_and_post_lsff_summaries_afe` calculates the pre and post fortification intake supplies, fortification vehicle reach and Inadequacy Summaries.

```{r eval=FALSE}
library(effectivenessCalculations)

calculate_pre_and_post_lsff_summaries_afe(
    householdConsumptionDf = householdConsumption,
    householdDetailsDf = householdDetails,
    nctListDf = nctList,
    intakeThresholdsDf = intakeThresholds,
    aggregationGroup = c("admin0Name", "admin1Name"),
    fortifiableFoodItemsDf = createFortifiableFoodItemsTable(),
    foodVehicleName = "wheat flour",
    fortificationLevels = fortificationLevels,
    years = c(2021:2024),
    MNList = c("A")
)
```

```{r eval=FALSE}
calculate_pre_and_post_lsff_summaries_cnd(
  householdConsumptionDf = householdConsumption,
  householdDetailsDf = householdDetails,
  nctListDf = nctList,
  intakeThresholdsDf = intakeThresholds,
  aggregationGroup = c("admin0Name", "admin1Name"),
  fortifiableFoodItemsDf = createFortifiableFoodItemsTable(),
  foodVehicleName = "wheat flour",
  fortificationLevelsDf = fortificationLevels,
  years = c(2021:2024),
  MNList = c("A")
)
```


